# Data transformation

```{r, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(tm)
library(tidytext)
library(textdata)

source("sentiment_analysis.R")
```

## Sentiment Analysis on Reddit Posts regarding GME

```{r echo=FALSE}
reddit_filenames <- list.files("data/raw/reddit/daywise", pattern="*.csv", full.names=TRUE)
reddit_df <- do.call(rbind,lapply(reddit_filenames, read.csv))
reddit_df <- subset(reddit_df, select = -c(X))
reddit_df <- reddit_df[!duplicated(reddit_df),]
```


```{r}
# filter posts with score > 10 and contains GME in title or text
reddit_GME_sa <- reddit_df %>%
  filter(score >= 10) %>%
  select(postid, created_utc, title, selftext) %>%
  mutate(title_contains_GME = grepl("GME", title, ignore.case = TRUE),
         text_contains_GME = grepl("GME", selftext, ignore.case = TRUE)) %>%
  filter(title_contains_GME | text_contains_GME) %>%
  mutate(date_utc = as.Date(as.POSIXct(as.numeric(created_utc), origin="1970-01-01")),
         text = cleanData(str_trim(paste(title, selftext))),
         postid = paste(postid, date_utc, sep = "_"))
```

```{r warning=FALSE}
reddit_GME_sa_Jan <- reddit_GME_sa %>%
  filter(date_utc <= as.Date('2021-01-31') & date_utc >= as.Date('2021-01-01')) %>%
  select(postid, text)

gme_nrc_Jan <- get_nrc_sentiments(reddit_GME_sa_Jan)
```

```{r warning=FALSE}
reddit_GME_sa_Feb <- reddit_GME_sa %>%
  filter(date_utc <= as.Date('2021-02-28') & date_utc >= as.Date('2021-02-01')) %>%
  select(postid, text)

gme_nrc_Feb <- get_nrc_sentiments(reddit_GME_sa_Feb)
```

```{r warning=FALSE}
reddit_GME_sa_567 <- reddit_GME_sa %>%
  filter(date_utc <= as.Date('2021-07-31') & date_utc >= as.Date('2021-05-01')) %>%
  select(postid, text)

gme_nrc_567 <- get_nrc_sentiments(reddit_GME_sa_567)
```

```{r}
gme_nrc_Jan_agg <- gme_nrc_Jan %>%
  select(textDate, sentiment, wordCount) %>%
  group_by(textDate, sentiment) %>%
  dplyr::summarise(wordCount = sum(wordCount)) 

gme_nrc_Feb_agg <- gme_nrc_Feb %>%
  select(textDate, sentiment, wordCount) %>%
  group_by(textDate, sentiment) %>%
  dplyr::summarise(wordCount = sum(wordCount)) 

gme_nrc_first_wave <- rbind(gme_nrc_Jan_agg, gme_nrc_Feb_agg)

write.csv(gme_nrc_first_wave, file = ("data/clean/reddit/gme_sa_nrc_first_wave.csv"), row.names=FALSE)
``` 


```{r}
gme_nrc_567_agg <- gme_nrc_567 %>%
  select(textDate, sentiment, wordCount) %>%
  group_by(textDate, sentiment) %>%
  dplyr::summarise(wordCount = sum(wordCount)) 

write.csv(gme_nrc_567_agg, file = ("data/clean/reddit/gme_sa_nrc_second_wave.csv"), row.names=FALSE)
```
```{r}
tmp_1 <-gme_nrc_Jan %>% 
  select(textWord, sentiment, wordCount) %>%
  group_by(textWord, sentiment) %>%
  dplyr::summarise(wordCount = sum(wordCount))%>%
  arrange(desc(wordCount))

tmp_567 <-gme_nrc_567 %>% 
  select(textWord, sentiment, wordCount) %>%
  group_by(textWord, sentiment) %>%
  dplyr::summarise(wordCount = sum(wordCount))%>%
  arrange(desc(wordCount))

```


## Google Trends Data Transformation
In the Google Trends source data, it assigns a number to each keyword for each period(week). The numbers represent search interest relative to the highest point on the chart for the given region and time. A value of 100 is the peak popularity for the term. A value of 50 means that the term is half as popular. A score of 0 means there was not enough data for this term. A score of <1 means there is some search interest but it's extremely low. We are replacing all <1's with 0.5, so that we can keep the data frame consistent with all scores as numeric data. 

We also need to tidy the dataset because some of the column names are not names of variables, but values of a variable: the original column names represent the values of the `keyword` variable and the values in the columns represents the values of `score`, and each row represents 5 observations, not one. To tidy the dataset, we make the offending columns into a new pair of variables using `pivot_longer`. 
```{r echo=FALSE}
combined_web_raw <- readr::read_csv("data/raw/gtrends/combined_web.csv")

combined_web_clean <- combined_web_raw %>%
  mutate(`r/WallStreetBets` = replace(`r/WallStreetBets`, `r/WallStreetBets` == "<1", 0.5)) %>%
  mutate(`r/WallStreetBets` = as.numeric(`r/WallStreetBets`)) %>%
  pivot_longer(cols = !Week,
             names_to = "keyword",
             values_to = "score"
             )
write.csv(combined_web_clean, file = ("data/clean/gtrends/combined_web.csv"),row.names=FALSE)

combined_news_raw <- readr::read_csv("data/raw/gtrends/combined_news.csv")
combined_news_clean <- combined_news_raw %>%
  mutate(`r/WallStreetBets` = replace(`r/WallStreetBets`, `r/WallStreetBets` == "<1", 0.5),
         `GameStop` = replace(`GameStop`, `GameStop` == "<1", 0.5)) %>%
  mutate(`r/WallStreetBets` = as.numeric(`r/WallStreetBets`),
         `GameStop` = as.numeric(`GameStop`)) %>%
  pivot_longer(cols = !Week,
             names_to = "keyword",
             values_to = "score"
             )
write.csv(combined_news_clean, file = ("data/clean/gtrends/combined_news.csv"),row.names=FALSE)
```

After cleaning, it contains 3 rows and 260 records.
```{r}
knitr::kable(data.frame(
                cols = c('week','keyword','score'),
                data_type = c('date', 'string', 'numeric'),
                description = c("Which week?","Search keyword","Search interest score")
              ), 
             col.names = c('Column', 'Type', 'Description'),
             row.names = F,font_size = 10)
```


## Reddit Data Transformation
There were 2 waves of sharp stock price change for WallStreetBets (WSBs) stocks in 2021, which were around January/Feburary and May/June period. These 2 waves are mainly caused by the discussion in the sub-Reddit group, WallStreetBets. Therefore, we have downloaded the Reddit posts that have been posted during these 2 periods and also extend some time before and after the wave. This is because we believe it takes some time for the initial posts to get public attention and then the posts starts to influence the stock price. Also, by including the posts that are slightly after the wave, we can do a comparison during and after the wave to check how big the effects of the posts in the sub-Reddit group on the stock price. Therefore, we have downloaded the data for the whole January, February, May, June and July, which have completely cover the 2 waves and also cover some extension. Also, we have parsed the posts on daily basis, which also helps to show the change over time.

Before starting to do the analysis, we need to find the list of WSB stocks first. the Generally speaking, all the stocks that have been discussed in the WallStreetBets sub-Reddit group should be considered as WSB stock. However, given the time frame that we considered is relatively long, which is 5 months, also, the WSBs has caught huge public attention, which also attracted a lot of new redditers. Therefore, there are many people participate in the discussion and the stocks mentioned are quite diversified. In this project, we will only focus on the top 10 stocks that have been mentioned in the posts. 

In the source data, which are the daily posts csv files, there are 2 columns that may contains the stock information, which are `title` and `selftext` respectively. Therefore, we need to first find the stock ticker from these 2 columns. Generally, the stock ticker should start with `$` and followed by 2 to 4 consecutive upper case letters. However, in the source data, there is no `$` exists, we cannot get the exact stock data but rather, we can extract out the list of possible stock tickers by extracting all the sub-strings which are consists of 2 to 4 consecutive upper case letters. 

We have used regex in python to extract out the list of possible stock tickers from `title` and `selftext` respectively for each of the daily reddit csv and then we combine these 2 lists together. However, there might be the case that the possible stock tickers are mentioned by the redditers both in `title` and `selftext`. In this case, we define that the possible stock ticker should be considered only once. Therefore, after combining the 2 lists together, we also need to drop duplicates to make sure there is no double count of possible stock ticker from both `title` and `selftext`. With that, we can make sure that the count of every possible stock ticker in 1 row is at most 1. 

Then, we start to count the possible stock ticker and summarize the count information into a dictionary. For every daily reddit csv, we will get a possible stock ticker count dictionary and combine them together to get the final count dictionary and stored it into the clean data folder. 

Now, in r, we can read the file which contains the information of the final possible stock ticker count. Since we are only interested in the top 10 WSB stocks, we need to re-order the data frame according to the word count in descending order. 

We noticed that there are some invalid tickers exists in the data frame, but that is expected since there is no perfect way to extract out the stock ticker due to the lack of `$` in the data source, so we manually go through the data frame and select out the top 10 tickers, which are: `GME`, `AMC`, `BB`,`NOK`, `SND`, `NAKD`, `PLTR`, `CLOV`, `RETA`, `MAR`, respectively.

```{r}
df <- read.csv('data/clean/reddit/possible_tickers_count.csv')
df %>% arrange(desc(count)) -> df
write.csv(df,"data/clean/reddit/ranked_possible_tickers_count.csv", row.names = FALSE)
```

