# Results
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(quantmod)
library(PerformanceAnalytics)
library(ggplot2)
library(plyr)
library(scales)
library(ggcorrplot)
library(reshape2)
library(plotly)
library(patchwork)
```


## What's the impact of r/wallstreetbet?

### General Public's interests on Google

#### Interest over time
```{r}
combined_web <- readr::read_csv("data/clean/gtrends/combined_web.csv")
combined_news <- readr::read_csv("data/clean/gtrends/combined_news.csv")

web <- combined_web %>%
  ggplot(aes(x=Week, y=score, color = keyword)) +
  geom_line() +
  ggtitle("Web Search Interest overtime")

news <- combined_news %>%
  ggplot(aes(x=Week, y=score, color = keyword)) +
  geom_line() +
  ggtitle("News Search Interest overtime")

web / news
```
The above two plots display the interest on the relative topics during the time period 2020-11-15 to 2021-11-15. Numbers represent search interest relative to the highest point on the chart for the given region and time. A value of 100 is the peak popularity for the term. A value of 50 means that the term is half as popular. A score of 0 means there was not enough data for this term.

#### Interest by subregion




