# Results
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(quantmod)
library(PerformanceAnalytics)
library(ggplot2)
library(plyr)
library(scales)
library(ggcorrplot)
library(reshape2)
library(plotly)
library(patchwork)
library(maps)
library(mapdata)
library(lubridate)
library(treemap)
library(wordcloud2)
library(highcharter)
```

```{r}
light_blue <- '#88A8F2'
light_red <- '#EF856E'
green <- "#8DF186"
purple <- "#D5A7F1"
```

## What's the impact of r/wallstreetbet?

## Stock Data and Information
### Stock Data Plot
The most representative WSB stocks are `GME` and `AMC`. Also, these 2 stocks are the top 2 most widely discussed stocks in WallStreetBet sub-reddit analysed in Chapter 3 - cleaning. Therefore, we choose these 2 stocks and show the stock price and volume change in the past one year.

The graph is interactive, where we can choose select the period of time that we want to focus on by dragging on the bottom graph. This allows us to zoom in and see the graph clearly. Also, we can choose the specific period, i.e. the past 1 year or past 6 months data by pressing the corresponding buttons above and we can easily go back to the main graph by pressing the "RESET" botton.

```{r}
getSymbols("GME",src='yahoo')
df_GME <- data.frame(Date=index(GME),coredata(GME))

# Generate Bollinger Bands
bbands <- BBands(GME[,c("GME.High","GME.Low","GME.Close")])

df_GME <- subset(cbind(df_GME, data.frame(bbands[,1:3])), Date >= "2020-12-01")

for (i in 1:length(df_GME[,1])) {
  if (df_GME$GME.Close[i] >= df_GME$GME.Open[i]) {
      df_GME$direction[i] = 'Increasing'
  } else {
      df_GME$direction[i] = 'Decreasing'
  }
}
i <- list(line = list(color = 'green'))
d <- list(line = list(color = 'red'))

# candlestick chart
fig <- df_GME %>% plot_ly(x = ~Date, type="candlestick",
          open = ~GME.Open, close = ~GME.Close,
          high = ~GME.High, low = ~GME.Low, name = "GME",
          increasing = i, decreasing = d)
fig <- fig %>% add_lines(x = ~Date, y = ~up , name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands",
            hoverinfo = "none", inherit = F) 
fig <- fig %>% add_lines(x = ~Date, y = ~dn, name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands", inherit = F,
            showlegend = FALSE, hoverinfo = "none") 
fig <- fig %>% add_lines(x = ~Date, y = ~mavg, name = "Moving Avg",
            line = list(color = '#E377C2', width = 0.5),
            hoverinfo = "none", inherit = F) 
fig <- fig %>% layout(yaxis = list(title = "Price"))

# volume chart
fig2 <- df_GME
fig2 <- fig2 %>% plot_ly(x=~Date, y=~GME.Volume, type='bar', name = "GME Volume",
          color = ~direction, colors = c('green','red')) 
fig2 <- fig2 %>% layout(yaxis = list(title = "Volume"))

# date slider 
rs <- list(visible = TRUE, x = 0.5, y = -0.055,
           xanchor = 'center', yref = 'paper',
           font = list(size = 9),
           buttons = list(
             list(count=1,
                  label='RESET',
                  step='all'),
             list(count=1,
                  label='1 YR',
                  step='year',
                  stepmode='backward'),
             list(count=6,
                  label='6 MO',
                  step='month',
                  stepmode='backward'),
             list(count=3,
                  label='3 MO',
                  step='month',
                  stepmode='backward'),
             list(count=1,
                  label='1 MO',
                  step='month',
                  stepmode='backward')
           ))

# combined plot
fig <- subplot(fig, fig2, heights = c(0.7,0.2), nrows=2,
             shareX = TRUE, titleY = TRUE)
fig <- fig %>% layout(title = paste("GME: 2020-12-01 -",Sys.Date()),
         xaxis = list(rangeselector = rs),
         legend = list(orientation = 'h', x = 0.5, y = 1,
                       xanchor = 'center', yref = 'paper',
                       font = list(size = 10),
                       bgcolor = 'transparent'))

fig
```

```{r}
getSymbols("AMC",src='yahoo')
df_AMC <- data.frame(Date=index(AMC),coredata(AMC))

# Generate Bollinger Bands
bbands <- BBands(AMC[,c("AMC.High","AMC.Low","AMC.Close")])

df_AMC <- subset(cbind(df_AMC, data.frame(bbands[,1:3])), Date >= "2020-12-01")

for (i in 1:length(df_AMC[,1])) {
  if (df_AMC$AMC.Close[i] >= df_AMC$AMC.Open[i]) {
      df_AMC$direction[i] = 'Increasing'
  } else {
      df_AMC$direction[i] = 'Decreasing'
  }
}
i <- list(line = list(color = 'green'))
d <- list(line = list(color = 'red'))

# candlestick chart
fig3 <- df_AMC %>% plot_ly(x = ~Date, type="candlestick",
          open = ~AMC.Open, close = ~AMC.Close,
          high = ~AMC.High, low = ~AMC.Low, name = "AMC",
          increasing = i, decreasing = d)
fig3 <- fig3 %>% add_lines(x = ~Date, y = ~up , name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands",
            hoverinfo = "none", inherit = F) 
fig3 <- fig3 %>% add_lines(x = ~Date, y = ~dn, name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands", inherit = F,
            showlegend = FALSE, hoverinfo = "none") 
fig3 <- fig3 %>% add_lines(x = ~Date, y = ~mavg, name = "Moving Avg",
            line = list(color = '#E377C2', width = 0.5),
            hoverinfo = "none", inherit = F) 
fig3 <- fig3 %>% layout(yaxis = list(title = "Price"))

# volume chart
fig4 <- df_AMC
fig4 <- fig4 %>% plot_ly(x=~Date, y=~AMC.Volume, type='bar', name = "AMC Volume",
          color = ~direction, colors = c('green','red')) 
fig4 <- fig4 %>% layout(yaxis = list(title = "Volume"))

# date slider 
rs <- list(visible = TRUE, x = 0.5, y = -0.055,
           xanchor = 'center', yref = 'paper',
           font = list(size = 9),
           buttons = list(
             list(count=1,
                  label='RESET',
                  step='all'),
             list(count=1,
                  label='1 YR',
                  step='year',
                  stepmode='backward'),
             list(count=6,
                  label='6 MO',
                  step='month',
                  stepmode='backward'),
             list(count=3,
                  label='3 MO',
                  step='month',
                  stepmode='backward'),
             list(count=1,
                  label='1 MO',
                  step='month',
                  stepmode='backward')
           ))

# combined plot
fig3 <- subplot(fig3, fig4, heights = c(0.7,0.2), nrows=2,
             shareX = TRUE, titleY = TRUE)
fig3 <- fig3 %>% layout(title = paste("AMC: 2020-12-01 -",Sys.Date()),
         xaxis = list(rangeselector = rs),
         legend = list(orientation = 'h', x = 0.5, y = 1,
                       xanchor = 'center', yref = 'paper',
                       font = list(size = 10),
                       bgcolor = 'transparent'))

fig3
```

From the above 2 graphs, we can clearly see that there are 2 waves of the WSB stocks, which are indicated by the sudden spike of the stock price as well as the sudden increase of the volume. These 2 waves are around January - Feburary and May - June period respectively. These 2 graphs actually double confirm with our previous claims. 

Also, the gray and red line in the price graph is the Bollinger Bands, which is the price level at 1 standard deviation level above and below the sample moving average of the price, which is able to capture the volatility of the stock. Generally, Bollinger bands is used to check whether prices are relatively high or low as comparing to the historical price. Here, we can see that for the beginning of the 2 waves, the price of both `GME` and `AMC` break the Bollinger upper bands, which suggests that the price of these 2 stocks are extremely high as comparing to the historical data. However, the Bollinger bands also adjusted themselves quickly to accommodate the sudden price change, so we can see that the price of these 2 stocks fall back within the Bollinger bands after a short period of time.

### Stock Risk Assessment
While the previous 2 graphs mainly focus on the price and volume aspects, there is one more aspect that are very important to the stock, which is risk. Risk can be measured by the standard deviation. Here, we would like to explore how the risk of the 2 stocks change before and after the 2 waves, which are `GME` and `AMC` respectively. Thus, we need to calculate the moving standard deviation of the 2 stocks over time.

Here, we take the closing price to be the one calculating the moving standard deviation since closing price is the most representative price among all the 5 prices. For each month, it is about 4 weeks and the stock market only opens in weekdays, thus, there are about 4*5 = 20 days with stock data every month. Therefore, we set the moving window to be 20, which is roughly about 1 month time. 

Also, we take the data since the start of last year because we want to see whether there is any difference in terms of the risk of `GME` and `AMC` by comparing the moving standard deviation before and after the 2 waves.
```{r}
getSymbols("GME",src='yahoo')
df_GME <- data.frame(Date=index(GME),coredata(GME))

df_GME <- subset(df_GME, Date >= "2020-01-01")
df_GME['moving_std'] <- rollapply(df_GME['GME.Close'], width = 20, FUN = sd, na.pad = TRUE)
ggplot(df_GME, aes(x=Date, y=moving_std)) +
  geom_line() +
  xlab("Date") +
  ylab('Moving Standard Deviation') + 
  ggtitle('Change of risk of GME over time')
```

```{r}
getSymbols("AMC",src='yahoo')
df_AMC <- data.frame(Date=index(AMC),coredata(AMC))

df_AMC <- subset(df_AMC, Date >= "2020-01-01")
df_AMC['moving_std'] <- rollapply(df_AMC['AMC.Close'], width = 20, FUN = sd, na.pad = TRUE)
ggplot(df_AMC, aes(x=Date, y=moving_std)) +
  geom_line() +
  xlab("Date") +
  ylab('Moving Standard Deviation') + 
  ggtitle('Change of risk of AMC over time')
```

From the 2 graphs above, we have following observations:

1. Around Jan/Feb and May/June period, there are huge changes for both `GME` and `AMC` in terms of risk.

2. `GME` has relatively higher risk than  `AMC` as `GME`'s moving standard deviation reached more than 100 while the highest moving standard deviation of `AMC` is about 13.

3. The risk of `GME` is highest in the first wave during Jan/Feb period while the risk of `AMC` is highest in the second wave during May/Jun period. This can be supported by the general knowledge that `GME` is the leading stock in the 1st wave while `AMC` is the leading stock in the 2nd wave.

### Most Popular Stocks
Besides studying about the 2 most representative stocks in WSBs, which are `GME` and `AMC` respectively, we could also study some other WSB stocks, which are not as popular as `GME` and `AMC` but they are still very representative and have received a lot of public attention.

Therefore, we extend our study to the top 10 mentioned stocks in the posts of WallStreetBets sub-reddit group. These 10 stocks has been identified in the Chapter 3 - Cleaning, which are: `GME`, `AMC`, `BB`, `NOK`, `SND`, `NAKD`, `PLTR`, `CLOV`, `RETA`, `MAR`, respectively.

Now, we can plot bar chart to show the count of posts that have mentioned about the stock for each stock.

```{r}
df <- read.csv('data/clean/reddit/ranked_possible_tickers_count.csv')
top_10_tickers <- c('GME','AMC','BB','NOK','SND','NAKD','PLTR','CLOV','RETA','MAR')
df %>% filter(possible_ticker %in% top_10_tickers) %>%
    ggplot(aes(x = fct_reorder(possible_ticker, desc(count)), y = count)) +
    geom_bar(stat = "identity") +
    ggtitle("Number of Posts Mentioned the Stock Ticker") +
    xlab("Stock Ticker") + 
    ylab("Count")
```

```{r}
df %>% 
  filter(possible_ticker %in% top_10_tickers) %>%
  mutate(ticker=paste(possible_ticker, count, sep ="\n"))%>%
  treemap(index = c("ticker"), vSize = "count", vColor = "count", type = "value", title = "Ticker mentions count")
```

From the graph above, we can see that `GME` and `AMC` are the dominant 2 dominant stocks that were discussed in WallStreeBets sub-reddit, which appears in around `r round(df$count[1]/sum(df$count)*100, 4)`% and `r round(df$count[2]/sum(df$count)*100, 4)`% of the total posts respectively. However, ``BB`, `NOK`, `SND` and the other stocks have also received some public attention, which are worthwhile to include them in the future analysis to get a bigger and clearer picture regarding the WSB stocks.

### Time Series of the Top 10 Stocks
Now, we want to study how the top 10 stocks' prices move over the past one year. Again, since the closing price is the most representative price among all the 5 prices, we just use closing price to calculate the daily return change over time. The equation used to calculate the daily stock return is that: `(current closing price - previous closing price) / previous closing price * 100%`.

```{r}
df_price <- read.csv('data/clean/stock/top_10_stocks_daily_return.csv')
df_price %>%
  select(Date, Symbol, Daily_return) %>%
  filter(Date >= as.Date('2021-01-01')) %>%
  filter(Date <= as.Date('2021-09-01')) %>%
  filter(Symbol != "^GSPC") %>%
  pivot_wider(names_from = Symbol, values_from = Daily_return, values_fill = 0) %>%
  gather(key = "variable", value = "value", -Date) -> df_price

df_price$Date <- as.Date(df_price$Date)

ts1 <- df_price %>%
  hchart("line",hcaes(x = Date, y = value, 
                      group = variable)) %>%
  hc_chart(zoomType = "x") %>%
  hc_colors(c("steelBlue", "sienna", "seaGreen", "teal", "violet", 
                       "orange", "darkSlateGray", "darkOrchid", "darkRed", "coral", "crimson")) %>%
  hc_legend(align = "center", verticalAlign = "bottom",layout = "horizontal") %>%
  hc_xAxis(title = list(text = "Date"),
           labels = list(format = '{value:%b %d}')) %>%
  hc_yAxis(title = list(text = "Daily Return (%)"),
           tickInterval = 20,
           max = 400) %>%
  hc_title(text = "<b>Daily Return of Top 10 mentioned Stocks</b>") %>%
  hc_subtitle(text = "Click and drag in the plot area to zoom in on a time span") %>%
  hc_plotOptions(area = list(lineWidth = 0.5)) 

ts1
```

From the above graph, we can have the following observation:

1. `AMC` has the highest daily return in the end of January 2021, which was around 300% increase as comparing to the previous day price. 

2. `GME` and `AMC`'s price change start to fluctuate a lot since the mid of the January, which marks the beginning of the WSB 1st wave. During this period, they started to get public attention.

3. In 27th Jan, the 1st wave of WSB reaches the peak, where `GME`, `AMC`, `BB`, `NOK`, `NAKD` achieved their highest daily return change on the same day.

4. Generally, the change in daily return in the 1st WSB wave is higher than the change in daily return in the 2nd WSB wave. This occurs since the price of the stocks has increases a lot in the first wave already, so in terms of the return (%), it is very hard to have as big change as that in 1st wave.

5. The stocks are included in different waves, while`PLTR` is the stock that is only active in 1st wave, there are other stocks that are active only in the 2nd wave, which are `CLOV`, `SND`, `RETA` respectively. For `GME`, `AMC`, `BB`, `NOK`, `NAKD`, they are active in both of the waves. However, for `MAR`, its stock price does not change much through out the 2 waves.

### Correlations between top 10 mentioned stocks
We removed `CLOV` from the ticker for 2020, because it went public in 2021.
```{r}
top_10_tickers <- c('GME','AMC','BB','NOK','SND','NAKD','PLTR','CLOV','RETA','MAR')

# remove CLOV
top_10_tickers_2020 <- c('GME','AMC','BB','NOK','SND','NAKD','PLTR','RETA','MAR')
ticker_vol <- NULL
for (ticker in top_10_tickers_2020)
  ticker_vol <- cbind(ticker_vol, getSymbols(ticker, src = "yahoo", from = "2020-01-01", to = "2020-12-31", auto.assign=FALSE)[,5])

drop_na <- apply(ticker_vol,1,function(x) all(!is.na(x)))
ticker_vol <- ticker_vol[drop_na]
colnames(ticker_vol) <- top_10_tickers_2020

corr <- cor(ticker_vol)
ggcorrplot(corr, 
           type = 'upper',
           lab = TRUE,
           lab_size = 3,
           method = 'circle',
           colors = c("red", "white", "green"),
           title="2020",
           legend.title = "Correlation")

```

```{r}
ticker_vol_wsb <- NULL
for (ticker in top_10_tickers)
  ticker_vol_wsb <- cbind(ticker_vol_wsb, getSymbols(ticker, src = "yahoo", from = "2021-01-01", to = "2021-02-01", auto.assign=FALSE)[,5])

drop_na <- apply(ticker_vol_wsb,1,function(x) all(!is.na(x)))
ticker_vol_wsb <- ticker_vol_wsb[drop_na]
colnames(ticker_vol_wsb) <- top_10_tickers

corr_wsb <- cor(ticker_vol_wsb)

ggcorrplot(corr_wsb,
           type = 'upper',
           lab = TRUE,
           lab_size = 3,
           method = 'circle',
           colors = c("red", "white", "green"),
           title="2021 Jan and Feb",
           legend.title = "Correlation")

```


## r/WallStreetBets Reddit Post Data

### r/WallStreetBets metrics

```{r}
reddit_sub <- readr::read_csv("data/clean/reddit/reddit_sub_growth.csv") %>%
  mutate(Date = as.Date(Date, format = "'%Y-%m-%d'"))

reddit_sub %>%
  hchart("line",hcaes(x = Date, y = growth)) %>%
  hc_chart(zoomType = "x") %>%
  hc_colors(c(light_blue)) %>%
  hc_legend(align = "center", verticalAlign = "bottom",layout = "horizontal") %>%
  hc_xAxis(title = list(text = "Date"),
           labels = list(format = '{value:%b %d}')) %>%
  hc_yAxis(title = list(text = "Subscriber growth")) %>%
  hc_title(text = "<b>r/WallStreetBets subscriber growth by Date</b>") %>%
  hc_subtitle(text = "Click and drag in the plot area to zoom in on a time span") %>%
  hc_plotOptions(area = list(lineWidth = 0.5)) %>% 
  hc_exporting(enabled = TRUE)
```

```{r}
reddit_post_ov <- readr::read_csv("data/clean/reddit/wsb_subreddit_overview.csv") %>%
  # select(date_utc, post_cnt, )
  rename(Date = date_utc) %>%
  pivot_longer(!Date, names_to = "attribute", values_to = "value")

reddit_post_ov_ts <- reddit_post_ov %>%
  hchart("line",hcaes(x = Date, y = value, group = attribute)) %>%
  hc_chart(zoomType = "x") %>%
  hc_colors(c(light_blue, light_red, green, purple)) %>%
  hc_legend(align = "center", verticalAlign = "bottom",layout = "horizontal") %>%
  hc_xAxis(title = list(text = "Date"),
           labels = list(format = '{value:%b %d}')) %>%
  hc_yAxis(title = list(text = "Subscriber growth")) %>%
  hc_title(text = "<b>r/WallStreetBets Daily active users and posts count</b>") %>%
  hc_subtitle(text = "Click and drag in the plot area to zoom in on a time span") %>%
  hc_plotOptions(area = list(lineWidth = 0.5)) %>% 
  hc_exporting(enabled = TRUE)


hc_add_annotation(
    reddit_post_ov_ts,
    labelOptions = list(
      backgroundColor = 'rgba(0,0,0,0.4)',
      verticalAlign = 'top',
      y = 15
    ),
    labels = list(
      list(point = list(xAxis = 0, yAxis = 0,
          x = datetime_to_timestamp(as.Date("2021/01/28")),
          y = 170000), text = "First wave"),
      list(point = list(xAxis = 0, yAxis = 0,
          x = datetime_to_timestamp(as.Date("2021/06/03")),
          y = 17000), text = "Second wave")
    )
)
```

### Reddit metrics vs. stock price
```{r}

AMC_2021 <- getSymbols('AMC', src="yahoo", from = "2021-01-01", auto.assign = FALSE)
amc_price_diff <- data.frame(Date=index(AMC_2021),coredata(AMC_2021)) %>%
  select(Date, ends_with("Close")) %>%
  rename(price = ends_with("Close")) %>%
  mutate(price_diff = price - lag(price)) %>%
  select(Date, price_diff)

amc_reddit_post <- readr::read_csv("data/clean/reddit/wsb_subreddit_overview.csv") %>%
  rename(Date = date_utc) %>%
  select(Date, amc_cnt)
  
amc_post_vs_diff <- merge(amc_reddit_post, amc_price_diff) %>%
  drop_na() 

amc_scatter <- ggplot(amc_post_vs_diff, aes(x = amc_cnt, 
                          y = price_diff))+
  geom_point(color = light_red) +
  geom_text(
    aes(label = ifelse(amc_cnt >= 3000 | price_diff>= 10 | price_diff <=-10, as.character(Date), "")),
    hjust=0.5, vjust=0, size=2) +
  labs(x = "# of posts in r/WallStreetBets", 
       y = "daily price change", 
       title = "AMC")+
  theme_bw() +
  theme(plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(face = "bold", color = "grey35"),
        plot.caption = element_text(color = "grey68"),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position="bottom",
        legend.title = element_text(face="bold"))
```
```{r}
GME_2021 <- getSymbols('GME', src="yahoo", from = "2021-01-01", auto.assign = FALSE)
gme_price_diff <- data.frame(Date=index(GME_2021),coredata(GME_2021)) %>%
  select(Date, ends_with("Close")) %>%
  rename(price = ends_with("Close")) %>%
  mutate(price_diff = price - lag(price)) %>%
  select(Date, price_diff)

gme_reddit_post <- readr::read_csv("data/clean/reddit/wsb_subreddit_overview.csv") %>%
  rename(Date = date_utc) %>%
  select(Date, gme_cnt)
  
gme_post_vs_diff <- merge(gme_reddit_post, gme_price_diff) %>%
  drop_na() 

gme_scatter <- ggplot(gme_post_vs_diff, aes(x = gme_cnt, 
                          y = price_diff))+
  geom_point(color = light_blue) +
  geom_text(
    aes(label = ifelse(gme_cnt >= 10000 | price_diff >= 50 | price_diff <=-50, as.character(Date), "")),
    hjust=0.5, vjust=0, size=2) +
  labs(x = "# of posts in r/WallStreetBets", 
       y = "daily price change", 
       title = "GME")+
  theme_bw() +
  theme(plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(face = "bold", color = "grey35"),
        plot.caption = element_text(color = "grey68"),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position="bottom",
        legend.title = element_text(face="bold"))

amc_gme <- amc_scatter + gme_scatter

amc_gme + plot_annotation(
  title = 'Post count vs daily price change scatterplot',
  subtitle = 'Jan, Feb, May, Jun, July 2021',
)
```


### What are the most popular words?
```{r}
reddit_wc <- readr::read_csv("data/clean/reddit/reddit_wc_total.csv")
wordcloud2(data=reddit_wc, size=0.7, maxRotation = 0, minRotation = 0)
```


### Sentiment analysis on Reddit posts regarding GME
```{r echo=FALSE, message=FALSE}
gme_nrc_first_wave <- readr::read_csv("data/clean/reddit/gme_sa_nrc_first_wave.csv")
gme_nrc_second_wave <- readr::read_csv("data/clean/reddit/gme_sa_nrc_second_wave.csv")
neg_sentiments = c('anger', 'disgust', 'fear', 'negative', 'sadness')
```
```{r}
first_wave <- gme_nrc_first_wave %>%
  select(sentiment, wordCount) %>%
  group_by(sentiment) %>%
  dplyr::summarise(wordCount = sum(wordCount)) %>%
  mutate(label = ifelse(sentiment %in% neg_sentiments, 'neg', 'pos')) %>%
  ggplot(aes(x = fct_reorder(sentiment, desc(wordCount)), y = wordCount)) +
    geom_bar(stat = "identity", aes(fill = label)) +
    scale_fill_manual(values = c("neg" = green,
                                "pos" = light_red)) +
    ggtitle("GME Sentiment Jan and Feb") +
    xlab("sentiment")
second_wave <- gme_nrc_second_wave %>%
  select(sentiment, wordCount) %>%
  group_by(sentiment) %>%
  dplyr::summarise(wordCount = sum(wordCount)) %>%
  mutate(label = ifelse(sentiment %in% neg_sentiments, 'neg', 'pos')) %>%
  ggplot(aes(x = fct_reorder(sentiment, desc(wordCount)), y = wordCount)) +
    geom_bar(stat = "identity", aes(fill = label)) +
    scale_fill_manual(values = c("neg" = green,
                                "pos" = light_red)) +
    ggtitle("GME Sentiment May, Jun and Jul") +
    xlab("sentiment")
first_wave / second_wave
```

```{r}
gme_nrc_total <- rbind(gme_nrc_first_wave, gme_nrc_second_wave)
gme_nrc_sum <- gme_nrc_total %>%
  mutate(label = ifelse(sentiment %in% neg_sentiments, 'neg', 'pos')) %>%
  group_by(textDate, label) %>%
  summarise(wordCount = sum(wordCount)) %>%
  ungroup() %>%
  pivot_wider(id_cols = textDate, names_from = label, values_from = wordCount) %>%
  mutate(positive_percentage = pos/(pos+neg)) %>%
  mutate(positive_percentage = (positive_percentage - min(positive_percentage))/(max(positive_percentage)-min(positive_percentage))*100) %>%
  select(textDate, positive_percentage)
textDate <- seq(as.Date("2021/3/1"), as.Date("2021/5/30"), "days")
empty_df <- data.frame(textDate)
empty_df$positive_percentage <- NA
gme_nrc_sum <- rbind(gme_nrc_sum, empty_df)
gme_stock <- getSymbols("GME", src="yahoo", from = "2021-01-01", to = "2021-07-31", auto.assign = FALSE)
gme_stock_df <- data.frame(Date=index(gme_stock),coredata(gme_stock)) %>% 
  mutate(price = (GME.Close - min(GME.Close))/(max(GME.Close)-min(GME.Close))*100) %>%
  select(Date, price)
total <- merge(gme_stock_df, gme_nrc_sum, by.y="textDate", by.x="Date") %>%
  pivot_longer(!Date, names_to = "attr", values_to = "val")
ggplot(total, aes(x=Date, y=val, color=attr)) +
  geom_line() +
  scale_color_manual(values = c(light_blue, light_red)) +
  ggtitle("GME positive percentage and stock price") +
  ylab("value") +
  labs(color = "") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold"),
        plot.caption = element_text(color = "grey68"),
        legend.position="bottom")
```

Above plot analyzes if the sentiments on r/WallStreetBets had any impact on GME's stock price.


### General Public's interests on Google

We believe that the whole event , i.e. r/wallstreetbets subreddit, short squeeze and the associated stocks are relatively new to the public, therefore, they are very likely to search some of the related keywords in Google to understand the whole event. Therefore, in this section, we would like to use the Google search related data to explore the general public attention towards this event. 

#### Interest over time

In Google, people can search in the website and if they already know the basic information about the event and they follow the event closely and only interested in the most recent news, therefore, we would like to zoom one level down into Google News to understand the topics that the close followers are interested in.

We have identified some keywords from the word cloud based on the size of the words there. However, there are some commonly searched word in our daily life, i.e. stock, market, buy and etc, so we need to exclude them from the list. Therefore, we choose `GME`, `AMC`, `wallStreetBet`, `reddit`, `robinhood` to be the key words. However, in the source data, there are misalignment in the word format, i.e. Google data source use `GameStop` to represent `GME`, so we choose the closest word form, which are: `AMC`,`GameStop`, `r/WallStreetBets`,`Reddit`,`Robinhood` respectively. 

Also, since we want to compare the public interest towards these key words before and after the events in order to show how big the effect of the event on the public interest, we choose to display the data during the time period 2020-11-15 to 2021-11-15.

```{r}
combined_web <- readr::read_csv("data/clean/gtrends/combined_web.csv")
combined_news <- readr::read_csv("data/clean/gtrends/combined_news.csv")

web <- combined_web %>%
  ggplot(aes(x=Week, y=score, color = keyword)) +
  geom_line() +
  ggtitle("Web Search Interest overtime")

news <- combined_news %>%
  ggplot(aes(x=Week, y=score, color = keyword)) +
  geom_line() +
  ggtitle("News Search Interest overtime")

web / news
```
In the above 2 graphs, the x-axis is the date. For the y-aixs score, it represents search interest relative to the highest point on the chart for the given region and time. A value of 100 is the peak popularity for the term. A value of 50 means that the term is half as popular. A score of 0 means there was not enough data for this term.

From the above 2 graphs, we have the following observations:

1. This event has attract huge public attention around the end of Jan, 2021 and start of Feb, 2021 period of time.

2. `GME` caught the highest attention during the 1st wave of the WSB, while `AMC` caught the highest attention during the 2nd wave of the WSB.

3. Generally, the 1st wave of WSB caught more public attention than the 2nd wave of WSB.

4. For the professionals and the closely followed people, more news reported the `GME` and `Robinhood` related topics, since they are the one using `Robinhood` to trade `GME`. While for the general public, they are more care about the different stocks, i.e. `GME` and `AMC`.

5. `Reddit` always has relatively high search interest, which indicates that there are constant active users in `Reddit`, while for `r/WallStreetBets`, before and after the event, only very few people use it. Therefore, the active users in this sub-reddit is not very high, which coincident with our previous conclusion from the daily active user graph.