# Results
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(quantmod)
library(PerformanceAnalytics)
library(ggplot2)
library(plyr)
library(scales)
library(ggcorrplot)
library(reshape2)
library(plotly)
library(patchwork)
```


## What's the impact of r/wallstreetbet?

### General Public's interests on Google

#### Interest over time
```{r}
combined_web <- readr::read_csv("data/clean/gtrends/combined_web.csv")
combined_news <- readr::read_csv("data/clean/gtrends/combined_news.csv")

web <- combined_web %>%
  ggplot(aes(x=Week, y=score, color = keyword)) +
  geom_line() +
  ggtitle("Web Search Interest overtime")

news <- combined_news %>%
  ggplot(aes(x=Week, y=score, color = keyword)) +
  geom_line() +
  ggtitle("News Search Interest overtime")

web / news
```
The above two plots display the interest on the relative topics during the time period 2020-11-15 to 2021-11-15. Numbers represent search interest relative to the highest point on the chart for the given region and time. A value of 100 is the peak popularity for the term. A value of 50 means that the term is half as popular. A score of 0 means there was not enough data for this term.

#### Interest by subregion





#### Stock Data Plot
The most Representative WSB stocks are `GME` and `AMC`. Also, these 2 stocks are the top 2 most widely discussed stocks in WallStreetBet sub-reddit analysed in Chapter 3 - cleaning. Therefore, we choose these 2 stocks and show the stock price and volume change in the past one year.

```{r}
getSymbols("GME",src='yahoo')
df_GME <- data.frame(Date=index(GME),coredata(GME))

# Generate Bollinger Bands
bbands <- BBands(GME[,c("GME.High","GME.Low","GME.Close")])

df_GME <- subset(cbind(df_GME, data.frame(bbands[,1:3])), Date >= "2020-12-01")

for (i in 1:length(df_GME[,1])) {
  if (df_GME$GME.Close[i] >= df_GME$GME.Open[i]) {
      df_GME$direction[i] = 'Increasing'
  } else {
      df_GME$direction[i] = 'Decreasing'
  }
}
i <- list(line = list(color = 'green'))
d <- list(line = list(color = 'red'))

# candlestick chart
fig <- df_GME %>% plot_ly(x = ~Date, type="candlestick",
          open = ~GME.Open, close = ~GME.Close,
          high = ~GME.High, low = ~GME.Low, name = "GME",
          increasing = i, decreasing = d)
fig <- fig %>% add_lines(x = ~Date, y = ~up , name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands",
            hoverinfo = "none", inherit = F) 
fig <- fig %>% add_lines(x = ~Date, y = ~dn, name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands", inherit = F,
            showlegend = FALSE, hoverinfo = "none") 
fig <- fig %>% add_lines(x = ~Date, y = ~mavg, name = "Moving Avg",
            line = list(color = '#E377C2', width = 0.5),
            hoverinfo = "none", inherit = F) 
fig <- fig %>% layout(yaxis = list(title = "Price"))

# volume chart
fig2 <- df_GME
fig2 <- fig2 %>% plot_ly(x=~Date, y=~GME.Volume, type='bar', name = "GME Volume",
          color = ~direction, colors = c('green','red')) 
fig2 <- fig2 %>% layout(yaxis = list(title = "Volume"))

# date slider 
rs <- list(visible = TRUE, x = 0.5, y = -0.055,
           xanchor = 'center', yref = 'paper',
           font = list(size = 9),
           buttons = list(
             list(count=1,
                  label='RESET',
                  step='all'),
             list(count=1,
                  label='1 YR',
                  step='year',
                  stepmode='backward'),
             list(count=6,
                  label='6 MO',
                  step='month',
                  stepmode='backward'),
             list(count=3,
                  label='3 MO',
                  step='month',
                  stepmode='backward'),
             list(count=1,
                  label='1 MO',
                  step='month',
                  stepmode='backward')
           ))

# combined plot
fig <- subplot(fig, fig2, heights = c(0.7,0.2), nrows=2,
             shareX = TRUE, titleY = TRUE)
fig <- fig %>% layout(title = paste("GME: 2020-12-01 -",Sys.Date()),
         xaxis = list(rangeselector = rs),
         legend = list(orientation = 'h', x = 0.5, y = 1,
                       xanchor = 'center', yref = 'paper',
                       font = list(size = 10),
                       bgcolor = 'transparent'))

fig
```

```{r}
getSymbols("AMC",src='yahoo')
df_AMC <- data.frame(Date=index(AMC),coredata(AMC))

# Generate Bollinger Bands
bbands <- BBands(AMC[,c("AMC.High","AMC.Low","AMC.Close")])

df_AMC <- subset(cbind(df_AMC, data.frame(bbands[,1:3])), Date >= "2020-12-01")

for (i in 1:length(df_AMC[,1])) {
  if (df_AMC$AMC.Close[i] >= df_AMC$AMC.Open[i]) {
      df_AMC$direction[i] = 'Increasing'
  } else {
      df_AMC$direction[i] = 'Decreasing'
  }
}
i <- list(line = list(color = 'green'))
d <- list(line = list(color = 'red'))

# candlestick chart
fig3 <- df_AMC %>% plot_ly(x = ~Date, type="candlestick",
          open = ~AMC.Open, close = ~AMC.Close,
          high = ~AMC.High, low = ~AMC.Low, name = "AMC",
          increasing = i, decreasing = d)
fig3 <- fig3 %>% add_lines(x = ~Date, y = ~up , name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands",
            hoverinfo = "none", inherit = F) 
fig3 <- fig3 %>% add_lines(x = ~Date, y = ~dn, name = "Bollinger Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands", inherit = F,
            showlegend = FALSE, hoverinfo = "none") 
fig3 <- fig3 %>% add_lines(x = ~Date, y = ~mavg, name = "Moving Avg",
            line = list(color = '#E377C2', width = 0.5),
            hoverinfo = "none", inherit = F) 
fig3 <- fig3 %>% layout(yaxis = list(title = "Price"))

# volume chart
fig4 <- df_AMC
fig4 <- fig4 %>% plot_ly(x=~Date, y=~AMC.Volume, type='bar', name = "AMC Volume",
          color = ~direction, colors = c('green','red')) 
fig4 <- fig4 %>% layout(yaxis = list(title = "Volume"))

# date slider 
rs <- list(visible = TRUE, x = 0.5, y = -0.055,
           xanchor = 'center', yref = 'paper',
           font = list(size = 9),
           buttons = list(
             list(count=1,
                  label='RESET',
                  step='all'),
             list(count=1,
                  label='1 YR',
                  step='year',
                  stepmode='backward'),
             list(count=6,
                  label='6 MO',
                  step='month',
                  stepmode='backward'),
             list(count=3,
                  label='3 MO',
                  step='month',
                  stepmode='backward'),
             list(count=1,
                  label='1 MO',
                  step='month',
                  stepmode='backward')
           ))

# combined plot
fig3 <- subplot(fig3, fig4, heights = c(0.7,0.2), nrows=2,
             shareX = TRUE, titleY = TRUE)
fig3 <- fig3 %>% layout(title = paste("AMC: 2020-12-01 -",Sys.Date()),
         xaxis = list(rangeselector = rs),
         legend = list(orientation = 'h', x = 0.5, y = 1,
                       xanchor = 'center', yref = 'paper',
                       font = list(size = 10),
                       bgcolor = 'transparent'))

fig3
```

From the above 2 graphs, we can clearly see that there are 2 waves of the WSB stocks, which are indicated by the sudden spike of the stock price as well as the sudden increase of the volume. These 2 waves are around January - Feburary and May - June period respectively. These 2 graphs actually double confirm with our previous claims. 

Also, the gray and red line in the price graph is the Bollinger Bands, which is the price level at 1 standard deviation level above and below the sample moving average of the price, which is able to capture the volatility of the stock. Generally, Bollinger bands is used to check whether prices are relatively high or low as comparing to the historical price. Here, we can see that for the beginning of the 2 waves, the price of both `GME` and `AMC` break the Bollinger upper bands, which suggests that the price of these 2 stocks are extremely high as comparing to the historical data. However, the Bollinger bands also adjusted themselves quickly to accommodate the sudden price change, so we can see that the price of these 2 stocks fall back within the Bollinger bands after a short period of time.

#### Stock Risk Assessment
While the previous 2 graphs mainly focus on the price and volume aspect 